Sensitivity of He Flames in X-ray Bursts to Nuclear Physics

### 2023-07-19 xrb5/paper.tex
update

%\documentclass[12pt, preprint]{aastex}
\documentclass[preprint,times,tighten]{aastex631}

@@

%======================================================================
% Introduction
%======================================================================
\section{Introduction}\label{Sec:Introduction}

An X-ray burst (XRB) is a thermonuclear runaway caused by the ignition of the accreted fuel on the surface of a neutron star. Through Roche-lobe overflow, accreted matter is transferred from the companion star's envelope to the surface of the neutron star. The companion star is likely to have a similar composition to the Sun, i.e.\ a mixture of hydrogen, helium, and a small fraction of carbon, nitrogen, and oxygen \citep{Galloway_2020_basics_of_xrb}. Nuclear explosions are directly affected by the initial composition of the accreted layer and the accretion rate. XRBs found with a mixture of hydrogen and helium fuel layers show bursts with $\sim 5$ sec rise time, while a pure helium layer is typically more explosive and shows bursts with shorter rise times ($\sim 1$ sec). If the shell is enriched with carbon rather than helium, then the explosion is likely to have an extended rise duration, from minutes to hours known as a superburst \citep{Kuulkers_2002,Cumming_2001,Gupta_2007}. 
% This is in contrast to a few seconds in the case of regular type I XRBs, which are XRBs that have a rapid rise time followed by a gradual decline in the light curve. \MarginPar{this last sentence seems redundant}

Since the timescale of accretion between each burst is in the order of $10^4$ secs while the rise time is in the order of $\sim 1 - 10$ sec \citep{Parikh_2013}, it is unlikely for the same thermodynamic condition to exist on the entire surface of the neutron star and for the entire surface to start burning simultaneously \citep{Shara_1982}. Therefore, nuclear ignition is likely to begin in a localized region, and spread to the rest of the neutron star \citep{Spitkovsky_2002}. This asymmetrical burning leads to modulations in the observed flux during the rotation of neutron stars, which causes asymmetrical surface brightness during XRBs \citep{strohmayer_2009}. This explains burst oscillation behavior, a millisecond period variation of XRB intensity during rise time, and the double-peak light curve for non-photospheric-radius-expansion XRBs discovered and supported by observational data \citep{Altamirano_2010,Chakraborty_2014,Bhattacharyya_2006, Kaaret_2007,Smith_1997}.

@@

Our simulation setup is the same as described in \citep{eiden:2020, harpole:2021}, so here we only reiterate the essential points. The simulations are performed using a 2D r-z cylindrical geometry, assuming azimuthal symmetry. 
The hydrodynamics is evolved using an unsplit piecewise parabolic method \citep{ppm,ppmunsplit,millercolella:2002}.
We work with a corotating frame, and assume a rotational frequency $\Omega = 1000$ Hz for the neutron star.  Gravity is assumed to be constant, since the accreted layer is thin.  Our initial model is also unchanged from our previous papers.  We employ a hydrostatic initial model to represent the neutron star's initial thermodynamic conditions, with a hot model in the left part of the domain and a cool model in the right---this drives a rightward propagating flame (a spreading hotspot for our geometry).  By default, reactions are incorporated using
operator-splitting.

@@

A reaction rate cross section, $\sigma$, takes the form:
\begin{equation}
    \sigma(E) = \frac{S(E)}{E} e^{-2\pi \eta}
\end{equation}
where $S(E)$ contains the details of the nuclear physics, $E$ is the energy of particle collisions in the center-of-mass frame, and $\eta$, accounts for Coulomb barrier penetration due to quantum effects \citep{Newton2007}. The reaction rate, $R_{\textrm{th}}$, is found by integrating the cross-section over the Maxwellian velocity distribution.  If the nuclei involved in the reaction are present in a high-density region that is permeated with plasma particles, then the strength of the Coulomb barrier would be reduced due to the plasma screening effect since the effective charge of the fusing nuclei are reduced. The screening enhancement factor is usually expressed as
\begin{equation}
    F_{\textrm{scr}} = \exp{(h)}
\end{equation}
where $h$ is a function that characterizes the screening magnitude. Therefore, the overall screened nuclear reaction rate is defined as
\begin{equation}\label{Eq:screened_rate}
    R_{\textrm{scr}} = F_{\textrm{scr}}R_{\textrm{th}}
\end{equation}

@@

{\tt SCREEN5} is the name of a widely-circulated screening routine (originally written in Fortran) that was the original screening routine used by \castro.
The overall procedure of {\tt SCREEN5} is summarized in the appendix of \cite{Wallace:1982}. In {\tt SCREEN5}, we define $\Gamma = (2/(Z_1+Z_2))^{1/3}Z_1 Z_2 \Gamma_e$, where $\Gamma_e = e^2\sqrt[3]{(4\pi n_e/3)}/(k_BT)$ describes the thermodynamic condition at which the reaction takes place, $Z$ is the charge of the fusing nuclei, $\mu_{12}$ is the reduced mass for the two fusing nuclei, $e$ is the electron charge, $n_e$ is the electron number density, and $k_B$ is Boltzmann's constant. When the plasma screening effect is weak or $\Gamma < 0.3$, {\tt SCREEN5} utilizes the equation proposed by \cite{Graboske_1973, Dewitt_1973}, which assumes that the interacting nuclei are separated by zero distance. To account for the spatial dependence of the screening enhancement factor, a more precise description of the strong plasma screening limit is utilized when $\Gamma > 0.8$. In \cite{jancovici:1977}, a quadratic dependence of the separation distance between the interacting nuclei was shown. This idea was applied to a one-component plasma by \cite{alastuey:1978}. By following a similar procedure outlined in \cite{itoh:1979}, the screening routine for one-component plasma can be extended to a multi-component plasma, which is suitable for a general mixture of ions. Finally, in
the intermediate screening regime, $0.3 < \Gamma < 0.8$, a weighted average between the weak and strong screening enhancement functions is used.

@@

{\tt aprox13} & {\tt aprox13} & Strang-splitting & {\tt SCREEN5} \\
{\tt subch\_full} & {\tt subch\_full} & Strang-splitting & {\tt SCREEN5} \\
{\tt subch\_full\_mod} & {\tt subch\_full\_mod} & Strang-splitting & {\tt SCREEN5} \\
{\tt subch\_simple} & {\tt subch\_simple} & Strang-splitting & {\tt SCREEN5} \\
{\tt aprox13\_sdc} & {\tt aprox13} & simplified SDC & {\tt SCREEN5} \\
{\tt subch\_full\_sdc} & {\tt subch\_full} & simplified SDC & {\tt SCREEN5} \\
{\tt aprox13\_chu} & {\tt aprox13} & Strang-splitting & {\tt CHUGUNOV2007}

@@

\begin{figure*}
\centering
\plotone{network_abar_50ms.pdf}
\caption{\label{fig:network_abar_50ms} Slice plots comparing $\Bar{A}$ for {\tt aprox13} (top panel), {\tt subch\_full} (second panel from top), {\tt subch\_full\_mod} (third panel), and {\tt subch\_simple} (last panel) at 50 ms. }
\end{figure*}

\begin{figure*}
\centering
\plotone{network_enuc_50ms.pdf}
\caption{\label{fig:network_enuc_50ms} Slice plots comparing $\dot{e}_{\textrm{nuc}}$ for {\tt aprox13} (top panel), {\tt subch\_full} (second panel from top), {\tt subch\_full\_mod} (third panel), and {\tt subch\_simple} (last panel) at 50 ms.}
\end{figure*}

@@

\begin{figure*}
    \centering
    \plotone{network_aprox13_nuc_frac.pdf}
    \caption{\label{fig:network_aprox13_nuc} Slice plots showing the mass fractions of ${}^{12}$C, ${}^{16}$O, and ${}^{28}$Si for {\tt aprox13} at 20 ms.}
\end{figure*}

\begin{figure*}
    \centering
    \plotone{network_subch_nuc_frac.pdf}
    \caption{\label{fig:network_subch_nuc} Slice plots showing the mass fractions of ${}^{12}$C, ${}^{16}$O, and ${}^{28}$Si for {\tt subch\_full} at 20 ms.}
\end{figure*}

\begin{figure*}
    \centering
    \plotone{network_subch_mod_nuc_frac.pdf}
    \caption{\label{fig:network_subch_mod_nuc} Slice plots showing the mass fractions of ${}^{12}$C, ${}^{16}$O, and ${}^{28}$Si for {\tt subch\_full\_mod} at 20 ms.}
\end{figure*}

@@

\begin{figure*}
    \centering
    \plotone{network_species_summary_log.pdf}
    \caption{\label{fig:network_species_summary} The overall evolution of the total mass for ${}^{12}$C, ${}^{16}$O, ${}^{20}$Ne, ${}^{24}$Mg, ${}^{28}$Si, and ${}^{32}$S for the 4 simulations models: {\tt aprox13}, {\tt subch\_full}, {\tt subch\_full\_mod}, and {\tt subch\_simple}.}
\end{figure*}

@@

\begin{figure*}
    \centering
    \plotone{network_u_v_enuc_25ms.pdf}
    \plotone{network_u_v_enuc_100ms.pdf}
    \caption{\label{fig:network_u_v_enuc} $u-v$ phase plots for {\tt aprox13} (panels in the first column on the left), {\tt subch\_full} (second column), {\tt subch\_full\_mod} (third column), {\tt subch\_simple} (fourth column) at $t = 25$ ms (top 4 panels) and $t = 100$ ms (bottom 4 panels). The x-axis, $u$, shows the velocity in the $r$ direction, whereas the y-axis, $v$, shows the velocity in the $z$ direction. The color bar shows $\dot{e}_{\textrm{nuc}}$.}
\end{figure*}

@@

\begin{table*}
\caption{\label{Tab:network_fitted_param}
Fitted parameters of the fitting functions Eq. \ref{Eq:quadratic_fit} and \ref{Eq:tanh_fit} for {\tt aprox13}, {\tt subch\_full}, {\tt subch\_full\_mod}, and {\tt aprox13\_chu}. The fitting function is applied for $t > 8$ ms.
}

@@

@@

{\tt subch\_full\_mod} & $58.53 \pm 0.24$ & $2.122 \pm 0.016$ & $0.7773 \pm 0.0004$ & N/A & N/A & N/A \\

@@

\begin{table*}
\caption{\label{Tab:network_instan_vel}
Instantaneous flame propagation speed at $t = 23$ ms and $t = 100$ ms for {\tt aprox13}, {\tt subch\_full}, {\tt subch\_full\_mod}, {\tt subch\_simple}, and {\tt aprox13\_chu}. $t = 23$ ms and $t=100$ ms represent the acceleration phase for {\tt subch\_full} and {\tt subch\_simple} and the steady phase at the late-stage, respectively. $t_{10}$ represents the theoretical time for the flame to reach 10 km.
}

\begin{ruledtabular}
\footnotesize
\centering
%\resizebox{1\textwidth}{!}{
\begin{tabular}{cccc}
\small 
Name &
$v_{23}$ [$\mbox{km} \ \mbox{s}^{-1}$] &
$v_{100}$ [$\mbox{km} \ \mbox{s}^{-1}$] &
$t_{10}$ [s]
\\
\colrule

{\tt aprox13} & $3.369 \pm 0.016$ & $5.234 \pm 0.027$ & 0.7647 \\
{\tt subch\_full} & $20.732 \pm 0.284$ & $5.411 \pm 0.105$ & 0.9917 \\
{\tt subch\_full\_mod} & $3.468 \pm 0.017$ & $7.975 \pm 0.029$ & 0.4873 \\
{\tt subch\_simple} & $21.095 \pm 0.332$ & $5.521 \pm 0.120$ & 0.8483 \\
{\tt aprox13\_chu} & $3.106 \pm 0.014$ & $4.874 \pm 0.024$ & 0.7912 \\
% {\tt aprox13\_sdc} & $3.039 \pm 0.014$ & $5.201 \pm 0.024$ & $5.764 \pm 0.027$\\
% {\tt subch\_full\_sdc} & $19.811 \pm 0.248$ & $5.181 \pm 0.096$ & $5.228 \pm 0.108$\\
\end{tabular}
%}
\end{ruledtabular}
\end{table*}

Using the fitted parameters, the instantaneous speed of the flame front at different times can be calculated, as shown in Table \ref{Tab:network_instan_vel}. We observe that during the acceleration burst phase at $t = 23$ ms, the difference in the instantaneous speed between {\tt subch\_full} and {\tt subch\_simple} can be as much as 7 times higher compared to the other two simulations. Furthermore, {\tt subch\_full\_mod} accelerates towards the end since it still has a sufficient amount of ${}^{12}$C fuel due to the inefficient reaction flows to ${}^{16}$O. Even though the flame front for {\tt subch\_full\_mod} is expected to surpass {\tt subch\_full} and {\tt subch\_simple} at $t \sim 160$ ms, based on Figure \ref{fig:network_front}, $\dot{e}_{\textrm{nuc}}$ from Figure \ref{fig:network_time_profile} appears to reach its peak at $120$ ms. Therefore, there is no guarantee that the lateral propagating flame for {\tt subch\_full\_mod} would exceed its counterparts.

Assuming that the fitting functions accurately describe the flame propagation, the expected time for the flame to reach a typical neutron star radius of 10 km, $t_{10}$, can be calculated, as shown in Table \ref{Tab:network_instan_vel}. $t_{10}$ serves as a rough prediction for the rise time of XRBs with a pure ${}^{4}$He accretion layer. $t_{10}$ for all models are $\lesssim 1$ sec, whereas $t_{10}$ for {\tt subch\_full} is $\sim 1$ sec, consistent with previous observational studies \citep{galloway:2008}.

@@

\begin{figure*}
\centering
\plotone{screen_temp_50ms.pdf}
\caption{\label{fig:screen_temp} Slice plots comparing temperature for {\tt aprox13} (top panel) and {\tt aprox13\_chu} (bottom panel) at $t = 50$ ms.}
\end{figure*}

\begin{figure*}
\centering
\plotone{screen_gamma_50ms.pdf}
\caption{\label{fig:screen_gamma_50ms} Slice plots comparing $\Gamma_e$ for {\tt aprox13} (top panel) and {\tt aprox13\_chu} (bottom panel) at $t = 50$ ms.}
\end{figure*}

\begin{figure*}
\centering
\plotone{screen_gamma_100ms.pdf}
\caption{\label{fig:screen_gamma_100ms} Slice plots comparing $\Gamma_e$ for {\tt aprox13} (top panel) and {\tt aprox13\_chu} (bottom panel) at $t = 100$ ms.}
\end{figure*}

We now present a comparison between the effects of {\tt SCREEN5} and {\tt CHUGUNOV2007} screening routines on the dynamics of the propagating flame in XRBs. Figure \ref{fig:screen_temp} shows the temperature for {\tt aprox13} and {\tt aprox13\_chu} at $t = 50$ ms, which suggests that there are no significant differences in the flame structure between the two models. Figure \ref{fig:screen_gamma_50ms} and \ref{fig:screen_gamma_100ms} show $\Gamma_e$, a measure to determine the approximate screening regime for the flame, at $t = 50$ ms and $t = 100$ ms.

Although a general trend of decreasing $\Gamma_e$ is observed as the flame progress, it is noteworthy that there are more fusion processes involving heavier nuclei at later stages of burning. Assuming triple-$\alpha$ process, it can inferred that the Coulomb coupling parameter, $\Gamma \sim 0.05$ and $0.025$ for $t = 50$ ms and $t = 100$ ms. Meanwhile, for oxygen burning at $t = 50$ ms and 100 ms, $\Gamma \sim 0.48$ and $0.32$, respectively. These results indicate that helium burning occurs in the weak screening regime, while heavier nuclei burning processes occur in the intermediate screening regime and gradually transition into the weak regime.

\begin{figure*}
\centering
\plotone{screen_time_profile.pdf}
\caption{\label{fig:screen_profile} Time profiles showing the weighted temperature and energy generation rate of the burning front for {\tt aprox13} and {\tt aprox13\_chu}.}
\end{figure*}

>>>>

%\documentclass[12pt, preprint]{aastex}
\documentclass[preprint,times,tighten,linenumbers,trackchanges]{aastex631}

@@

%======================================================================
% Introduction
%======================================================================
\section{Introduction}\label{Sec:Introduction}
An X-ray burst (XRB) is a thermonuclear runaway caused by the ignition of the accreted fuel on the surface of a neutron star. Through Roche-lobe overflow, accreted matter is transferred from the companion star's envelope to the surface of the neutron star. The companion star is likely to have a similar composition to the Sun, i.e.\ a mixture of hydrogen, helium, and a small fraction of carbon, nitrogen, and oxygen \citep{Galloway_2020_basics_of_xrb}. Nuclear explosions are directly affected by the initial composition of the accreted layer and the accretion rate. XRBs found with a mixture of hydrogen and helium fuel layers show bursts with $\sim 5$ s rise time, while a pure helium layer is typically more explosive and shows bursts with shorter rise times ($\sim 1$ s). If the shell is enriched with carbon rather than helium, then the explosion is likely to have an extended rise duration, from minutes to hours known as a superburst \citep{Kuulkers_2002,Cumming_2001,Gupta_2007}. 
% This is in contrast to a few seconds in the case of regular type I XRBs, which are XRBs that have a rapid rise time followed by a gradual decline in the light curve. \MarginPar{this last sentence seems redundant}

Since the timescale of accretion between each burst is in the order of $10^4$ s while the rise time is in the order of $\sim 1 - 10$ s \citep{Parikh_2013}, it is unlikely for the same thermodynamic condition to exist on the entire surface of the neutron star and for the entire surface to start burning simultaneously \citep{Shara_1982}. Therefore, nuclear ignition is likely to begin in a localized region, and spread to the rest of the neutron star \citep{Spitkovsky_2002}. This asymmetrical burning leads to modulations in the observed flux during the rotation of neutron stars, which causes asymmetrical surface brightness during XRBs \citep{strohmayer_2009}. This explains burst oscillation behavior, a millisecond period variation of XRB intensity during rise time, and the double-peak light curve for non-photospheric-radius-expansion XRBs discovered and supported by observational data \citep{Altamirano_2010,Chakraborty_2014,Bhattacharyya_2006, Kaaret_2007,Smith_1997}.

@@

Our simulation setup is the same as described in \citep{eiden:2020, harpole:2021}, so here we only reiterate the essential points. The simulations are performed using a 2D r-z cylindrical geometry, assuming azimuthal symmetry. 
The hydrodynamics is evolved using an unsplit piecewise parabolic method \citep{ppm,ppmunsplit,millercolella:2002}.
We work with a corotating frame, and assume a rotational frequency $\Omega = 1000$ Hz for the neutron star.  Gravity is assumed to be constant, since the accreted layer is thin.  Our initial model is also unchanged from our previous papers.  We employ a hydrostatic initial model to represent the neutron star's initial thermodynamic conditions, with a hot model in the left part of the domain and a cool model in the right---this drives a rightward propagating flame (a spreading hotspot for our geometry). \edit1{The initial composition can be broadly divided into two large regions. The base region ($0 < z < 2000$ cm) is composed of pure ${}^{56}$Ni, representing the underlying neutron star. On the other hand, the region beyond $z > 2000$ cm consists of pure ${}^{4}$He to represent the accretion layer.} By default, reactions are incorporated using
operator-splitting.

\edit1{{\castro} uses the adaptive mesh refinement system from {\amrex} \citep{amrex_joss}. The same simulation domain of $r = 1.8432 \times 10^5$ cm and $z = 3.072 \times 10^4$ cm is used for all of our models. At the coarse grid, we again used $1152 \times 192$ zones or a coarse resolution of $160$ cm with two additional refinement levels with refinement ratios of 4 and 2. This means that the first refinement level is 4 times finer than the coarse level and the finest level is 2 times finer than the first level. This enables us to achieve a finest level with $9216 \times 1536$ zones, corresponding to a resolution of 20 cm. Grid refinement is limited to regions where $\rho > 2.5 \times 10^4 \ \textrm{g} \ \textrm{cm}^{-3}$ in order to avoid unnecessary computational costs. The total simulation time is $\sim 120$ ms to avoid flame propagating outside of the domain.}

@@

A reaction rate cross section, $\sigma$, takes the form:
\begin{equation}
    \sigma(E) = \frac{S(E)}{E} e^{-2\pi \eta}
\end{equation}
where $S(E)$ contains the details of the nuclear physics, $E$ is the energy of particle collisions in the center-of-mass frame, and $\eta$, accounts for Coulomb barrier penetration due to quantum effects \citep{Newton2007}. The reaction rate, $R_{\textrm{th}}$, is found by integrating the cross-section over the Maxwellian velocity distribution.  If the nuclei involved in the reaction are present in a high-density region that is permeated with plasma particles, then the strength of the Coulomb barrier would be reduced due to the plasma screening effect since the effective charge of the fusing nuclei \deleted{are} \edit1{is} reduced. The screening enhancement factor is usually expressed as
\begin{equation}
    F_{\textrm{scr}} = \exp{(h)}
\end{equation}
where $h$ is a function that characterizes the screening magnitude. Therefore, the overall screened nuclear reaction rate is defined as
\begin{equation}\label{Eq:screened_rate}
    R_{\textrm{scr}} = F_{\textrm{scr}}R_{\textrm{th}}
\end{equation}

@@

{\tt SCREEN5} is the name of a widely-circulated screening routine (originally written in Fortran) that was the original screening routine used by \castro.
The overall procedure of {\tt SCREEN5} is summarized in the appendix of \cite{Wallace:1982}. In {\tt SCREEN5}, \edit1{the Coulomb coupling parameter, $\Gamma$, is defined in Eq. \ref{Eq:gamma_eq}},

\begin{equation}\label{Eq:gamma_eq}
    \Gamma = \sqrt[3]{\frac{2}{Z_1+Z_2}}Z_1 Z_2 \Gamma_e
\end{equation}

\edit1{where $\Gamma_e$ describes the thermodynamic condition at which the reaction takes place and is defined in Eq. \ref{Eq:gamma_e_eq},}

\begin{equation}\label{Eq:gamma_e_eq}
    \Gamma_e = \sqrt[3]{\frac{4\pi n_e}{3}}\frac{e^2}{k_BT}
\end{equation}

\deleted{we define $\Gamma = (2/(Z_1+Z_2))^{1/3}Z_1 Z_2 \Gamma_e$, where $\Gamma_e = e^2\sqrt[3]{(4\pi n_e/3)}/(k_BT)$ describes the thermodynamic condition at which the reaction takes place,} $Z$ is the charge of the fusing nuclei, \deleted{$\mu_{12} = $ is the reduced mass for the two fusing nuclei,} $e$ is the electron charge, $n_e$ is the electron number density, and $k_B$ is Boltzmann's constant. When the plasma screening effect is weak or $\Gamma < 0.3$, {\tt SCREEN5} utilizes the equation proposed by \cite{Graboske_1973, Dewitt_1973}, which assumes that the interacting nuclei are separated by zero distance. To account for the spatial dependence of the screening enhancement factor, a more precise description of the strong plasma screening limit is utilized when $\Gamma > 0.8$. In \cite{jancovici:1977}, a quadratic dependence of the separation distance between the interacting nuclei was shown. This idea was applied to a one-component plasma by \cite{alastuey:1978}. By following a similar procedure outlined in \cite{itoh:1979}, the screening routine for one-component plasma can be extended to a multi-component plasma, which is suitable for a general mixture of ions. Finally, in
the intermediate screening regime, $0.3 < \Gamma < 0.8$, a weighted average between the weak and strong screening enhancement functions is used.

@@

{\tt aprox13} & {\tt aprox13} & Strang-splitting & {\tt SCREEN5} \\
{\tt subch\_full\_mod} & {\tt subch\_full\_mod} & Strang-splitting & {\tt SCREEN5} \\
{\tt subch\_full} & {\tt subch\_full} & Strang-splitting & {\tt SCREEN5} \\
{\tt subch\_simple} & {\tt subch\_simple} & Strang-splitting & {\tt SCREEN5} \\
{\tt aprox13\_chu} & {\tt aprox13} & Strang-splitting & {\tt CHUGUNOV2007}\\
{\tt aprox13\_sdc} & {\tt aprox13} & simplified SDC & {\tt SCREEN5} \\
{\tt subch\_full\_sdc} & {\tt subch\_full} & simplified SDC & {\tt SCREEN5} \\

@@

\begin{figure*}
\centering
\plotone{network_abar_50ms.pdf}
\caption{\label{fig:network_abar_50ms} Slice plots comparing $\Bar{A}$ for {\tt aprox13} (top panel), {\tt subch\_full\_mod} (second panel from top), {\tt subch\_full} (third panel), and {\tt subch\_simple} (last panel) at 50 ms. \edit1{The vertical scaling is stretched to provide better clarity in the vertical flame structure.}}
\end{figure*}

\begin{figure*}
\centering
\plotone{network_enuc_50ms.pdf}
\caption{\label{fig:network_enuc_50ms} Slice plots comparing $\dot{e}_{\textrm{nuc}}$ for various models at 50 ms. \edit1{The vertical scaling is stretched to provide better clarity in the vertical flame structure.}}
\end{figure*}

@@

\begin{figure*}
    \centering
    \plotone{network_aprox13_nuc_frac.pdf}
    \caption{\label{fig:network_aprox13_nuc} Slice plots showing the mass fractions of ${}^{12}$C, ${}^{16}$O, and ${}^{28}$Si for {\tt aprox13} at 20 ms. \edit1{The vertical scaling is stretched to provide better clarity in the vertical flame structure.}}
\end{figure*}

\begin{figure*}
    \centering
    \plotone{network_subch_mod_nuc_frac.pdf}
    \caption{\label{fig:network_subch_mod_nuc} Slice plots showing the mass fractions of ${}^{12}$C, ${}^{16}$O, and ${}^{28}$Si for {\tt subch\_full\_mod} at 20 ms. \edit1{The vertical scaling is stretched to provide better clarity in the vertical flame structure.}}
\end{figure*}

\begin{figure*}
    \centering
    \plotone{network_subch_nuc_frac.pdf}
    \caption{\label{fig:network_subch_nuc} Slice plots showing the mass fractions of ${}^{12}$C, ${}^{16}$O, and ${}^{28}$Si for {\tt subch\_full} at 20 ms. \edit1{The vertical scaling is stretched to provide better clarity in the vertical flame structure.}}
\end{figure*}

@@

\begin{figure*}
    \centering
    \plotone{network_species_summary_log.pdf}
    \caption{\label{fig:network_species_summary} The overall evolution of the total mass for ${}^{12}$C, ${}^{16}$O, ${}^{20}$Ne, ${}^{24}$Mg, ${}^{28}$Si, and ${}^{32}$S for the 4 simulations models: {\tt aprox13},  {\tt subch\_full\_mod}, {\tt subch\_full}, and {\tt subch\_simple}.}
\end{figure*}

@@

\begin{figure*}
    \centering
    \plotone{network_u_v_enuc_aprox13.pdf}
    \plotone{network_u_v_enuc_subch_full_mod.pdf}
    \plotone{network_u_v_enuc_subch_full.pdf}
    \plotone{network_u_v_enuc_subch_simple.pdf}
    %\plotone{network_u_v_enuc_25ms.pdf}
    %\plotone{network_u_v_enuc_100ms.pdf}
    \caption{\label{fig:network_u_v_enuc} $u-v$ phase plots for {\tt aprox13} \edit1{(panels in the first row), {\tt subch\_full\_mod} (second row), {\tt subch\_full} (third row), {\tt subch\_simple} (fourth row) at $t = 25$ ms (4 panels on the first column) and $t = 100$ ms (4 panels on the second column)}. The x-axis, $u$, shows the velocity in the $r$ direction, whereas the y-axis, $v$, shows the velocity in the $z$ direction. The color bar shows $\dot{e}_{\textrm{nuc}}$.}
\end{figure*}

@@

\begin{table*}
\caption{\label{Tab:network_fitted_param}
Fitted parameters of the fitting functions Eq. \ref{Eq:quadratic_fit} and \ref{Eq:tanh_fit} for {\tt aprox13}, \edit1{{\tt subch\_full\_mod}, {\tt subch\_full}}, and {\tt aprox13\_chu}. The fitting function is applied for $t > 8$ ms.
}

@@

{\tt subch\_full\_mod} & $58.53 \pm 0.24$ & $2.122 \pm 0.016$ & $0.7773 \pm 0.0004$ & N/A & N/A & N/A\\

@@

@@

\begin{table*}
\caption{\label{Tab:network_instan_vel}
Instantaneous flame propagation speed at $t = 23$ ms and $t = 100$ ms for {\tt aprox13}, \edit1{{\tt subch\_full\_mod}, {\tt subch\_full}}, {\tt subch\_simple}, \edit1{and {\tt aprox13\_chu} are represented by $v_{23}$ and $v_{100}$, respectively.} \edit1{The acceleration phase for {\tt subch\_full} and {\tt subch\_simple} and the steady phase at the late-stage are represented by $t = 23$ ms and $t = 100$ ms, respectively.} \deleted{$t = 23$ ms and $t=100$ ms represent the acceleration phase for {\tt subch\_full} and {\tt subch\_simple} and the steady phase at the late-stage, respectively.} \edit1{The theoretical time for the flame to reach 30 km is represented by $t_{30}$.} \deleted{$t_{10}$ represents the theoretical time for the flame to reach 10 km.}
}

\begin{ruledtabular}
\footnotesize
\centering
%\resizebox{1\textwidth}{!}{
\begin{tabular}{cccc}
\small 
Name &
$v_{23}$ [$\mbox{km} \ \mbox{s}^{-1}$] &
$v_{100}$ [$\mbox{km} \ \mbox{s}^{-1}$] &
$t_{30}$ [s]
\\
\colrule

{\tt aprox13} & $3.369 \pm 0.016$ & $5.234 \pm 0.027$ & $1.4419 \pm 0.0064$\\
{\tt subch\_full\_mod} & $3.468 \pm 0.017$ & $7.975 \pm 0.029$ & $0.9697 \pm 0.0019$ \\
{\tt subch\_full} & $20.732 \pm 0.284$ & $5.411 \pm 0.105$ & $2.0717 \pm 0.0749$ \\
{\tt subch\_simple} & $21.095 \pm 0.332$ & $5.521 \pm 0.120$ & $1.6918 \pm 0.0441$ \\
{\tt aprox13\_chu} & $3.106 \pm 0.014$ & $4.874 \pm 0.024$ & $1.4872 \pm 0.0060$ \\
% {\tt aprox13\_sdc} & $3.039 \pm 0.014$ & $5.201 \pm 0.024$ & $5.764 \pm 0.027$\\
% {\tt subch\_full\_sdc} & $19.811 \pm 0.248$ & $5.181 \pm 0.096$ & $5.228 \pm 0.108$\\
\end{tabular}
%}
\end{ruledtabular}
\end{table*}

Using the fitted parameters, the instantaneous speed of the flame front at different times can be calculated, as shown in Table \ref{Tab:network_instan_vel}. We observe that during the acceleration burst phase at $t = 23$ ms, the difference in the instantaneous speed between {\tt subch\_full} and {\tt subch\_simple} can be as much as 7 times higher compared to the other two simulations. Furthermore, {\tt subch\_full\_mod} accelerates towards the end since it still has a sufficient amount of ${}^{12}$C fuel due to the inefficient reaction flows to ${}^{16}$O. Even though the flame front for {\tt subch\_full\_mod} is expected to surpass {\tt subch\_full} and {\tt subch\_simple} at $t \sim 160$ ms, based on Figure \ref{fig:network_front}, $\dot{e}_{\textrm{nuc}}$ from Figure \ref{fig:network_time_profile} appears to reach its peak at $\sim 120$ ms. \deleted{Therefore, there is no guarantee that the lateral propagating flame for {\tt subch\_full\_mod} would exceed its counterparts} \edit1{In the event of extreme downturns in $\dot{e}_{\textrm{nuc}}$ in the future, there is no assurance that the lateral propagating flame for {\tt subch\_full\_mod} would surpass its counterparts.}

Assuming that the fitting functions accurately describe the flame propagation, the expected time for the flame to \deleted{reach a typical neutron star radius of 10 km} \edit1{propagate laterally across a neutron star with a radius of 10 km or $\pi R \sim 30$ km}, $t_{30}$, can be calculated, as shown in Table \ref{Tab:network_instan_vel}.  \edit1{The quantity $t_{30}$} \deleted{$t_{10}$} serves as a rough prediction for the rise time of XRBs with a pure ${}^{4}$He accretion layer. \edit1{A basic calculation shows that $t_{30}$} \deleted{$t_{10}$} for all models are \deleted{$\lesssim 1$ s} \edit1{$\lesssim 2$ s}, whereas \deleted{$t_{10}$} \edit1{$t_{30}$} for {\tt subch\_full} is \deleted{$\sim 1$ s} \edit1{$\sim 2$ s}, consistent with previous observational studies \citep{galloway:2008}. \edit1{Here we emphasize that $t_{30}$ is extrapolated beyond the data with the assumption that the flame has a sustained constant acceleration. However, this assumption may not hold true. For instance, in the case of {\tt subch\_full\_mod}, $\dot{e}_{\textrm{nuc}}$ already reaches its peak at 120 ms, indicating that the flame's acceleration is not constant. Therefore, $t_{30}$ only serves as an order-of-magnitude calculation.}

@@

\begin{figure*}
\centering
\plotone{screen_temp_50ms.pdf}
\caption{\label{fig:screen_temp} Slice plots comparing temperature for {\tt aprox13} (top panel) and {\tt aprox13\_chu} (bottom panel) at $t = 50$ ms. \edit1{The vertical scaling is stretched to provide better clarity in the vertical flame structure.}}
\end{figure*}

\begin{figure*}
\centering
\plotone{screen_gamma_e_50ms.pdf}
\caption{\label{fig:screen_gamma_50ms} Slice plots comparing $\Gamma_e$ for {\tt aprox13} (top panel) and {\tt aprox13\_chu} (bottom panel) at $t = 50$ ms. \edit1{The vertical scaling is stretched to provide better clarity in the vertical flame structure.}}
\end{figure*}

\begin{figure*}
\centering
\plotone{screen_gamma_e_100ms.pdf}
\caption{\label{fig:screen_gamma_100ms} Slice plots comparing $\Gamma_e$ for {\tt aprox13} (top panel) and {\tt aprox13\_chu} (bottom panel) at $t = 100$ ms. \edit1{The vertical scaling is stretched to provide better clarity in the vertical flame structure.}}
\end{figure*}

We now present a comparison between the effects of {\tt SCREEN5} and {\tt CHUGUNOV2007} screening routines on the dynamics of the propagating flame in XRBs. Figure \ref{fig:screen_temp} shows the temperature for {\tt aprox13} and {\tt aprox13\_chu} at $t = 50$ ms, which suggests that there are no significant differences in the flame structure between the two models. Figure \ref{fig:screen_gamma_50ms} and \ref{fig:screen_gamma_100ms} show $\Gamma_e$ \edit1{(defined in Eq. \ref{Eq:gamma_e_eq})}, \edit1{which} provides a measure to determine the approximate screening regime for the flame, at $t = 50$ ms and $t = 100$ ms.

Although a general trend of decreasing $\Gamma_e$ is observed as the flame progress, it is noteworthy that there are more fusion processes involving heavier nuclei at later stages of burning. Assuming triple-$\alpha$ process, it can inferred that the Coulomb coupling parameter \edit1{$\Gamma$ (defined in Eq. \ref{Eq:gamma_eq})} $\sim 0.05$ for $t = 50$ ms and $0.025$ for $t = 100$ ms. Meanwhile, for oxygen burning at $t = 50$ ms and 100 ms, $\Gamma \sim 0.48$ and $0.32$, respectively. These results indicate that helium burning occurs in the weak screening regime, while heavier nuclei burning processes occur in the intermediate screening regime and gradually transition into the weak regime.

% \begin{figure*}
% \centering
% \plotone{screen_time_profile.pdf}
% \caption{\label{fig:screen_profile} Time profiles showing the weighted temperature and energy generation rate of the burning front for {\tt aprox13} and {\tt aprox13\_chu}.}
% \end{figure*}

The comparison between {\tt aprox13} and {\tt aprox13\_chu} regarding the weighted temperature and energy generate rate is illustrated in Figure \edit1{\ref{fig:network_time_profile}}. This plot illustrates that overall the nuclear energy generation rate of {\tt aprox13} is higher and exhibits a faster increasing rate compared to {\tt aprox13\_chu}. At $t \sim 10$ ms, when the temperature of the two models are approximately equal, the difference in the nuclear energy generation rate indicates that {\tt SCREEN5} provides a stronger screening effect during the initial flame propagation phase compared to {\tt CHUGUNOV2007}.
